### 2023-09-19 3.Design/crossbar.tex
small change

The crossbar system, and in a more general manner, the entire system will require an external controller to control the enable flags that are required in the system. Adding such a system will increase the power consumption of the overall system. However, due to the slow (precision of about $1\mu s$) nature of those signals, the controller will be very low power, and won't change the overall power consumption of the final system.%TODO maybe move to final circuit

>>>>

The crossbar system, and in a more general manner, the entire system will require an external controller to control the enable flags that are required in the system. Adding such a system will increase the power consumption of the overall system. However, due to the slow (precision of about $1\mu s$) nature of those signals, the controller will be very low power, and won't change the overall power consumption of the final system. This controller is not needed for the simulation as everything is managed within Cadence's virtuoso. In the real circuit, the enable signals need to be controlled somehow.%TODO maybe move to final circuit
